# Reproducible Reseach: Peer Assessment 1  
## Loading and preprocessing the data
```{r}
dir = "/Users/Shawn/Documents/BigData/Coursea/5.Reproducible Research/"
setwd(dir)

activity <- read.csv("activity.csv")  
```
## Mean of total number of steps taken per day
```{r}
dir = "/Users/Shawn/Documents/BigData/Coursea/5.Reproducible Research/"
setwd(dir)

activity <- read.csv("activity.csv")  
```

```{r}
library(ggplot2)
tot_steps <- tapply(activity$steps, activity$date, FUN = sum, na.rm = TRUE)
hist(tot_steps, xlab="total number of steps taken each day")
mean(tot_steps, na.rm = TRUE)
median(tot_steps, na.rm = TRUE)
```
## Mean total number of steps taken per day
```{r}
Aversteps <- aggregate(x = list(steps = activity$steps),
                  by = list(interval = activity$interval), 
                  FUN = mean,
                  na.rm = TRUE)

d <- ggplot(data = Aversteps, aes(x = interval, y = steps))
plot <- d + geom_line() +
       ggtitle("Time series plot: 5-minute interval vs averaged across all days ") + 
       xlab("5-minute interval") + 
       ylab("averaged across all days")
```

## The 5-minute interval of Maximun number of steps 
```{r}
max.steps <- Aversteps[Aversteps$steps == max(Aversteps$steps), ][1]
```
## Calculate and report the total number of missing values in the dataset 
```{r}
sum(is.na(activity))
```
## Inputing missig values
```{r}
newactivity <- activity 
for(i in 1:nrow(newactivity)){
  if(is.na(newactivity$steps[i] == TRUE))
    newactivity$steps[i] <- Aversteps[which(newactivity$interval[i] == activity$interval[i]),]$steps
}
```
## Check the number of NA in new data set
```{r}
sum(is.na(newactivity))

plot_newactivity_steps <- ggplot(newactivity, aes(date, steps)) + geom_bar(stat = "identity",
                                                 colour = "grey",
                                                 fill = "grey",
                                                 width = 0.7) 

new_tot_steps <- aggregate(newactivity$steps, 
                           list(Date = newactivity$date), 
                           FUN = sum)
colnames(new_tot_steps) <- c("date","steps")
```

## Mean and median of the edited total steps per day
```{r}
mean_new_tot_steps <- mean(new_tot_steps$steps)
median_new_tot_steps <- median(new_tot_steps$steps)
```
## Mean and median of the orignal total steps per day
```{r}
mean_ori_tot_steps <- mean(tot_steps, na.rm = TRUE)
median_ori_tot_steps <- median(tot_steps, na.rm = TRUE)
```
## Comparision the orignal and new data set
```{r}
diff_mean = mean_new_tot_steps - mean_ori_tot_steps
diff_median = median_new_tot_steps - median_ori_tot_steps
```
## Differences in activity patterns between weekdays and weekends
```{r}
weekday_or_weekend <- function(date) {
  day <- weekdays(date)
  if (day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"))
    return("weekday")
  else if (day %in% c("Saturday", "Sunday"))
    return("weekend")
  else
    stop("invalid date")
}
newactivity$date <- as.Date(newactivity$date)
newactivity$day <- sapply(newactivity$date, FUN=weekday_or_weekend)


averages <- aggregate(steps ~ interval + day, data=newactivity, mean)
ggplot(averages, aes(interval, steps)) + geom_line() + facet_grid(day ~ .) +
  xlab("5-minute interval") + ylab("Number of steps")

```
